---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# On the creation of hexStickers for published R packages

  The purpose of this repository is to provide a couple of concrete examples sorrounding the creation of unique hexagonal package identifiers with the 'hexStickers' package.
  
### 1. Create or download background image for sticker
  
```{r}
## required packages
library(magick)
library(dplyr)
library(hexSticker)
```
  
### 2. Basic Image Processing
  
```{r}
img <- image_read("figures/gene.jpeg")

res <- img %>%
  image_convert("png") %>%
  image_resize("1080 x 200")%>%
  image_fill(color="#062047", point="+45")

res
```

### 3. Building the sticker itself 
  
```{r}
final_res <- sticker(res, package="GA", p_size = 15,
                   p_y = 1.5,
                   s_x=1, s_y=0.8, s_width=1.1,
                   s_height = 14,
                   filename="figures/stickerSample.png",
                   h_fill="#062047",
                   h_color = "#062047")
```
  
### 4. Export and save the sticker
  
```{r}
plot(final_res)
```
  
### Gallery

  Below are a couple of interesting hexStickers that I have created for personal projects - I am confident that this is only a shallow dive into the creation of these stickers. For further research, I would suggest diving deeper into the image-altering functions within the 'magick' pacakge. 
